---
title: "Midterm_Presentation"
author: "Mi Zhang, Peng Liu, Yuanming Leng, Qiannan Shen"
date: "11/2/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source('strawbData.R')
source('visualization_function.R')
```

# Introduction
Our strawberries dataset is taking from the United States Department of Agriculture (USDA) and the Pesticide dataset is from Haviland. The strawberry dataset consists the years of 2015, 2016, 2018, 2019 and states including California, Florida, New York, North Carolina, Oregon, and Washington. 

In order to make extramely large data more accessible, we had changed the column "value" to log scale.

We can see that the measurement unit in LB displays a large proportion of data and we will use the unit "MEASURE IN LB" as the main focus to analyze our data.  

```{r echo=FALSE}
GGally::ggpairs(strawb1, columns=c(3,6), aes(color=strawb1[,3], alpha = 0.5),lower=list(combo=wrap("facethist",  
binwidth=0.5)))


```

-The following map is an example showing that both California and Florida have a large amount of strawberry bearing in pounds as comparing to other states.

```{r}
map(years = "2019", 
    chemical = "NOP USDA CERTIFIED", measurement = "MEASURED IN LB")


```
# Questions 

After reviewing the summary of our dataset, we came up with following questions:
-
-
-

# Here is our first approach to the question #1. 

As you can see in the plot below, California and Florida are the two states where USDA collected large amount of data in each type of chemicals. We also noticed that California and Florida increasely used all kinds of chemicals in recent years. 

```{r}
plot1("MEASURED IN LB")

```

# Strawberries and Chemical Toxins 

After wrangled USDA Strawberries dataset with Pesticide dataset, we tried to figure out how chemicals can impact the production or sales of strawberries. Below, we are going to look at two plots for further analysis. 

```{r}
plot3("MEASURED IN LB")

```

```{r}
plot4("MEASURED IN LB","Bee.Toxins","CALIFORNIA")
```

```{r}
plot5("MEASURED IN LB","Bee.Toxins","CALIFORNIA","slight")

```