---
output: 
  revealjs::revealjs_presentation:
    template: temp_1.html
    theme: white
    highlight: pygments 
    css: reveal.css
    center: true
---


```{r setup, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(error=TRUE)

source(file = "strawbData.R", echo = FALSE)
source(file = "visualization_function.R", echo = FALSE)
source(file = "maps.R", echo = FALSE)

```

<section data-background-opacity=0.2
         data-background-image="images/coverpic.png"
         >


   <h1 style="margin-top:50px;text-align:center;color=black;font-family:charter;font-size:50px;">
Midterm Project: Strawberry and Chemicals</h1>

<p style="margin-top:200px;text-align:center;font-family:charter;font-size:35px;color=black">Mi Zhang, Peng Liu, Yuanming Leng, Qiannan Shen</p>

<!-- image source --  freepiks.com -->

</section>

# Data Cleaning for Strawberry {data-background="images/bg-01.png"}

- remove empty/missing values and reduce white space in the cells
- split column with multiple items to separated columns
- redefine "MEASURED IN CWT" by multiplying by 100
- make extreme large value more accessible by using log scale on "value"
- redefine value as production of strawberry


# Measurement units and value {data-background="images/bg-02.png"}

- Our major analysis is base on the measurement units, and our main focus is on "MEASURE IN LB"

- Let's explore our shiny.app (https://lemony.shinyapps.io/ma615-midterm/)


# Mouse-over map {data-background="images/bg-03.png"}

- California and Florida have higher amount of annual strawberry production in pounds than other states.

```{r echo=FALSE, warning= FALSE, fig.height=5}
mo_map("MEASURED IN LB", "INSECTICIDE")
```

# Annual value of Strawberry in each state {data-background="images/bg-04.png"}

- Showing that California and Florida increasingly used all kinds of chemicals on strawberry in recent years.

```{r fig.height= 4.5}
plot1("MEASURED IN LB")
```

# Data wrangling for Strawberry and Pesticides {data-background="images/bg-01.png"}

- drop empty rows/columns, remove white space
- rename colname of Pesticide to chemical in order to match the colname in strawberry data
- use toupper() to capitalize all chemical names 
- use pivot_longer() to make all toxins and levels into longer columns
- use inner_join() to wrangle Pesticide and Strawberry dataset


# Questions {data-background="images/bg-02.png"}

- Which toxin has higher strawberry production value?
- Which type of chemical is commonly related to toxicity?


# Toxin level changes over years {data-background="images/bg-03.png"}

- Bee toxins are related to larger strawberry production values.

```{r, echo=FALSE, warning = FALSE, fig.height=6}
p3 =plot3("MEASURED IN LB")
ggplotly(p3, tooltip="y")
```

# Comparing fungicide and insecticide related values {data-background="images/bg-04.png"}
- In both human and bee toxins, insecticide and fungicide seem to have even proportion in strawberry production values in California
```{r fig.height=4}
p4 <- plot4("MEASURED IN LB", "CALIFORNIA")
ggplotly(p4, tooltip="y")
```

# Further analysis for Florida {data-background="images/bg-01.png"}
- Florida shows that insecticide has higher proportion.
```{r fig.height=4}
p4 <- plot4("MEASURED IN LB", "FLORIDA")
ggplotly(p4, tooltip="y")
```

# Bee Toxin {data-background="images/bg-02.png"}
- But looking solely at bee toxins, insecticide chemicals have higher proportion in strawberry production value in California.
```{r fig.height=4}
p5 <- plot5("MEASURED IN LB","Bee.Toxins","CALIFORNIA")
ggplotly(p5, tooltip="y")
```

# Further Analysis for Florida {data-background="images/bg-03.png"}
- Confirmed that insecticide is more commonly related to toxicity
```{r fig.height=4}
p5 <- plot5("MEASURED IN LB","Bee.Toxins","FLORIDA")
ggplotly(p5, tooltip="y")
```

# Conclusion {data-background="images/bg-04.png"}

- California and Florida have higher strawberry production and more data are collected from those two states according to shiny display.
- Bee toxins are related to higher strawberry production values than human toxins.
- Insecticide is more commonly related to toxicity than fungicide in strawberry production.

# Thanks {data-background="images/bg-01.png"}

- Professor Haviland 
- TA Bruce 
- Our lovely MA-615 Classmates
- Our teammates

# Citations {data-background="images/bg-02.png"}

- Haviland's lectures
- https://www.r-graph-gallery.com
- https://r-lang.com
- https://stackoverflow.com
- https://shiny.rstudio.com/tutorial

